Envelope Estimation using Geometric Properties of a Discrete Real Signal

### 2021-04-30 Papers/01_Pulses_Envelope/PulsesEnvelope.tex
progress

@@

\begin{table}[H]
\centering
\begin{tabular}{lcccc}
\hline
\multicolumn{5}{c}{\textbf{Average error per frame}} \\
              & Present Work & Smoothing & Low pass & Hilbert \\ 
\hline
alto          & 0.073        & 0.083     & 0.083   & 0.082   \\
bend          & 0.009        & 0.015     & 0.015   & 0.014   \\
piano         & 0.005        & 0.006     & 0.006   & 0.005   \\
brass         & 0.024        & 0.035     & 0.035   & 0.033   \\
soprano       & 0.042        & 0.065     & 0.065   & 0.065   \\
spoken voice  & 0.024        & 0.037     & 0.037   & 0.034   \\
tom           & 0.003        & 0.005     & 0.005   & 0.005   \\
sinusoid      & 0.113        & 0.193     & 0.195   & 0.191   \\ 
\hline
Average       & 0.037        & 0.055     & 0.055   & 0.054  
\end{tabular}
\caption{Comparison of the average errors of the algorithm presented in this work with the most common methods of digital envelope identification. The discrete waves used were normalized between -1 and 1. The average is between the absolute value of those waves and the envelope divided by two.}
\label{table:Error_comparison}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{lcccc}
\hline
\multicolumn{5}{c}{\textbf{Time in seconds}} \\
              & Present Work & Smoothing & Low pass & Hilbert \\ 
\hline
alto          & 0.008        & 0.101     & 0.007   & 0.011   \\
bend          & 0.030        & 0.226     & 0.012   & 0.131   \\
piano         & 0.034        & 0.374     & 0.014   & 0.042   \\
brass         & 0.032        & 0.297     & 0.011   & 0.045   \\
soprano       & 0.177        & 0.735     & 0.027   & 0.566   \\
spoken voice  & 0.014        & 0.105     & 0.003   & 0.038   \\
tom           & 0.007        & 0.084     & 0.018   & 0.026   \\
sinusoid      & 0.007        & 0.091     & 0.005   & 0.011   \\ 
\hline
Average       & 0.039        & 0.252     & 0.012   & 0.109  
\end{tabular}
\caption{Comparison of the processing time of the algorithm presented in this work with the most common methods of digital envelope identification.}
\label{table:Time_comparison}
\end{table}

>>>>

% TODO proof curvature %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our problem is to derive a measure of the average curvature of a discrete curve from its oscillations in the vertical axis.
Recalling that we derived the points in P from the local maxima, there is no local maxima between p0 and p1, and the envelope between both of them doesnt go below the minimum of them.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{table}[H]
\centering
\begin{tabular}{lcccc}
\hline
\multicolumn{5}{c}{\textbf{Average error per frame}} \\
Signal & Present Work & Smoothing & Low pass & Hilbert \\ 
\hline
alto  & 0.001 & 0.337 & 0.342 & 0.163 \\
bend  & 0.000 & 0.029 & 0.030 & 0.008 \\
brass & 0.001 & 0.107 & 0.107 & 0.038 \\
nonperiodic & 0.000 & 0.211 & 0.158 & 0.000 \\
piano & 0.003 & 0.016 & 0.016 & 0.007 \\
sinusoid & 0.000 & 0.132 & 0.131 & 0.000 \\
soprano & 0.000 & 0.155 & 0.155 & 0.044 \\
spoken\_voice & 0.006 & 0.109 & 0.110 & 0.045 \\
tom   & 0.001 & 0.011 & 0.015 & 0.005 \\
\hline
Average & 0.001 & 0.123 & 0.118 & 0.035 \\
frac. of max. & 0.010 & 1.000 & 0.961 & 0.281 \\
\end{tabular}
\caption{Comparison of the average errors of the algorithm presented in this work with the most common methods of digital envelope identification. The discrete waves used were normalized between -1 and 1. The average is between the absolute value of those waves and the envelope divided by two.}
\label{table:Error_comparison}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{lcccc}
\hline
\multicolumn{5}{c}{\textbf{Time in seconds}} \\
Signal  & Present Work & Smoothing & Low pass & Hilbert \\ 
\hline
alto  & 0.010 & 0.096 & 0.007 & 0.006 \\
bend  & 0.009 & 0.146 & 0.005 & 0.067 \\
brass & 0.015 & 0.253 & 0.005 & 0.035 \\
nonperiodic & 0.002 & 0.064 & 0.003 & 0.007 \\
piano & 0.022 & 0.316 & 0.009 & 0.030 \\
sinusoid & 0.003 & 0.069 & 0.003 & 0.006 \\
soprano & 0.111 & 0.574 & 0.013 & 0.293 \\
spoken\_voice & 0.003 & 0.062 & 0.003 & 0.017 \\
tom   & 0.002 & 0.070 & 0.001 & 0.004 \\
\hline
Average & 0.020 & 0.183 & 0.005 & 0.052 \\
frac. of max. & 0.108 & 1.000 & 0.030 & 0.283 \\
\end{tabular}
\caption{Comparison of the processing time of the algorithm presented in this work with the most common methods of digital envelope detection.}
\label{table:Time_comparison}
\end{table}
